### 2023-10-30 main.tex
intermediate

\subsection{Duality for the integrable process on a line segment}\label{integrableChain-duality}
Here we consider the chain defined in Subsection \ref{subsection-description-process-LINE}. We recall that the geometry is a one dimensional chain with sites $\{1,\ldots,L\}$ where reservoirs are attached to $1$ and $L$. Now we assume the hard-core exclusion rule, i.e. $\nu=1$. The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of $gl(N)$. Duality result stated in Subsection \ref{statementDualitySubsection} can be adapted. The extra-sites are denoted by $0$ and $L+1$, and they are connected with sites $1$ and $L$ of the chain respectively. The matrix $R_{x}$ defined in \eqref{Revmatrix} 
reduces to the identity, therefore the relation between the generators of the algebra and its transposed reduces to
\begin{equation}\label{transpostionPropertyFund}
	e_{ab}^T= e_{ba}\dt
\end{equation}
Therefore, duality matrix reads
\begin{equation}
	D=\mathcal{D}_{0}\otimes\prod_{x=1}^{L}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\otimes \mathcal{D}_{L+1}
\end{equation}
where $\mathcal{D}_{0}$ and $\mathcal{D}_{L+1}$ are given in \eqref{dualityMatrix2}. 
The elements of this duality matrix are given by
\begin{equation}\label{ElementsDualityMatrixChain}
	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
\end{equation}
The dual Hamiltonian is
\begin{equation}
	\widetilde{H}=\widetilde{H}_{left}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{right}
\end{equation}
where $\mathcal{H}$ is defined in \eqref{H-corsivo} and 
\begin{equation}\label{boundary-H-dual-chain}
	\widetilde{H}_{left}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{0}\,e_{Na}^{1}-e_{aa}^{1}\right)\qquad 	\widetilde{H}_{right}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{L+1}\,e_{Na}^{L}-e_{aa}^{L}\right)\dt
\end{equation}
In the long-time limit the dual process voids the chain, i.e. all particles of types $\{1,\ldots,N-1\}$ are eventually absorbed at the extra-sites $0$ and $L+1$ and replaced by types $N$. We also notice that, up the the bosonic creation operators $(a^{\dagger})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular. This simplification will be crucial in Sections \ref{sectionIntegrabiliy}.\\

Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities. Consider a dual configuration $\bm{\hat{\xi}}:=\sum_{k=1}^{m}\delta_{s_{k}}^{y_{k}}$ where $s_{k}\in\{1,\ldots,N-1\}$ and $y_{k}\in\{1,\ldots,L\}$ such that $y_{k}<y_{k+1}$ for every $k\in\{1,\ldots,m\}$. Fix an arbitrary initial configuration $\bm{n}$, the elements \eqref{ElementsDualityMatrixChain} of the duality matrix computed in the dual configuration $\bm{\hat{\xi}}$ read
\begin{equation}
	D(\bm{n},\bm{\hat{\xi}})=\prod_{k=1}^{m}\mathbbm{1}_{\{n_{s_{k}}^{s_{k}}=1\}}\dt
\end{equation}
Denoting the $m$-point correlations by $\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}}\rangle_{stat}$ we have 
%To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$). Therefore, we have the following equalities
\begin{equation}\label{CorrelationByABS-prob}
	\begin{split}
	\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}}\rangle_{stat}&=\lim_{t\to \infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\hat{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\hat{\xi}}(t))\right]
	\\&=\sum_{c_{1}=0}^{1}\ldots \sum_{c_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}})
\end{split}
\end{equation}
where
\begin{equation}\label{absProbabilitiesIntegrable}
	\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(c_{k}\delta_{0}+(1-c_{k})\delta_{L+1}\right)\lvert \bm{\xi}(0)=\hat{\bm{\xi}}\right)
\end{equation}
 namely the joint probability of having, for all $k=1,\ldots,m$, $c_{k}$ particles of species $s_{k}$ at site $y_{k}$ are absorbed at left and $1-c_{k}$ of the same particles absorbed at right. Therefore, by computing these absorption probabilities we determine the arbitrary non-equilibrium steady state correlations of the integrable multi-species stirring process.

@@

with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. This notation is equivalent to the one introduced in Subsection \ref{subsectionGeneratorStr}. Indeed, assume that at site $x$ we have a particle of type $a\in\{1,\ldots,N\} $, then $|n^{x}\rangle$ is composed by zeros but in the component $n_{a}^{x}$ where there is $1$. Therefore, we can uniquely associate  $\tau_{x}=a$ to this $|n^{x}\rangle$, denoting the presence of the species $a$ at site $x$. With this notation, we have that 

@@

with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$. \\ \\

@@

	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}\right)|\mathbf{\bm{\tau}}\rangle

@@

We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutation relations. 

@@

Using the notation $\tau_{x}$, $|\bm{\tau}\rangle $ introduced in \eqref{notation} we have 

@@

@@

\begin{equation}
\begin{split}
\Psi^{''}(\tau_1,\ldots,\tau_L)&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2+L-\sum_{x=1}^{L}\delta_{\tau_{x}<N}\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+L-x-\sum_{j=x+1}^{L}\delta_{\tau_{j}<N}\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}\delta_{\tau_{j}<N}\right)}\\
&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(3+L-x-\sum_{j=x}^{L}\delta_{\tau_{j}<N}\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}\delta_{\tau_{j}<N}\right)}\\
&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}{\Gamma\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}\\
&=  \frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\\
% &=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\frac{1}{\Gamma(-1)} B(3+L-x-\sum_{j=x}^{L}\delta_{\tau_{x}<N},-1)\\
\end{split}
\end{equation}
The last factor only depends on the positions of particles $N$. The $\lambda$-factor depends only on the number of particles of types $1,\ldots,N-1$.

Looks like there is a mistake somewhere...

@@

@@

		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\prod_{x=1}^{L}\lambda_{\tau_{x}}^{c_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}
	\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\lambda_{\tau_{x}}^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}

@@

\textbf{Remark}: In equation \eqref{ABS} we observe that when $\tau_{x}=N$ we have just a contribution of a factor $1$ on the product over $x$. Indeed, the empty species does not produce changes in the correlations between the non-empty species. \\ \\
\textbf{Remark:} If we consider the case $N=2$ we have that, for an arbitrary configuration $\bm{\tau}$, we can identify $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites and the remaining $L-|\bm{\tau}|$ empty. We denote by $(x_{i})_{i\in\{1,\ldots,|\bm{\tau}|\}}$ the coordinates of the occupied sites. We introduce $q\in\{0,\ldots,|\bm{\tau}|\}$ and we rewrite \eqref{ABS} as

@@

\paragraph{Proof of formula \eqref{ABS-vect}} Using \eqref{S2-Inverse} we have $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$, thus we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$. Here it is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and then make explicitly the tensor product over the chain. Using the exponential series, the matrix $\mathcal{S}_{2}$ is given by 

@@

This is a new configuration at site $x$ where, if $x\in\{q_{1},\ldots,q_{i}\}$, the occupation $\tau_{x}$ is replaced by $N$, while it is left uncaged if $x\notin \{q_{1},\ldots,q_{i}\}$. The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation. } \\ By considering a fixed $\langle\bm{\tau}|$, and by using \eqref{goodTP-S2} we obtain 

@@

For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, by using equation \eqref{ResulsBasis}, we obtain 

@@

\end{equation} where we have used the fact that 
	\left(1+\sum_{j=x}^{L}\delta_{\mu_{j},N}\right) =\left(2+L-y-\sum_{j=x}^{L}(1-\delta_{\mu_{x},N})\right)\co
Introducing $c_{x}$ defined as 
	c_{x}(\mu_{x})=(1-\delta_{\mu_{x},N}) \qquad \forall x\in \{1,\ldots L\}\co
\begin{equation}\label{coefficients-psiSec}
	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}
where, for the sake of notation we left understood the dependence on $\mu_{x}$ of $c_{x}$.\\
We introduce the following notation
\begin{equation}\label{notation1}
    e_{ab}=e_{a}^{b}=\left(\delta_{ac}\delta_{bd}\right)_{c,d\in\{1,\ldots,N\}}\qquad \forall a,b\in \{1,\ldots,N\}
\begin{equation}\label{notation2}
    e_{ab}\otimes e_{cd}=e_{a,c}^{b,d}=\left(\delta_{(a,b),(e,f)}\delta_{(c,d),(g,h)}\right)_{e,f,g,h\in \{1,\ldots,N\}}\qquad \forall a,b,c,d\in \{1,\ldots,N\}
    that can be generalized for $e_{\tau_{1},\ldots,\tau_{L}}^{q_{1},\ldots,q_{L}}$ with $\tau_{1},\ldots,\tau_{L},q_{1},\ldots,q_{L}\in \{1,\ldots,N\}$. With this notation we have that

@@

		\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}

@@

	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\frac{1}{(1+L)!}\sum_{c_{1},\ldots,c_{m}=0}^{1}\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)
\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\frac{1}{(1+L)!}\sum_{c_{1},\ldots,c_{m}=0}^{1}\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{1-c_{k}}\beta_{s_{k}}^{c_{k}}\left(1+\sum_{j=k}^{m}c_{j}\right)
To check!

@@

\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=&

@@

Therefore, comparing this formula and \eqref{absProbabilitiesIntegrable}, we can determine the absorption probabilities 

>>>>

\subsection{Duality for the integrable process on a line segment}\label{integrableChain-duality}
Here we consider the chain defined in Subsection \ref{subsection-description-process-LINE}. We recall that the geometry is a one dimensional chain with sites $\{1,\ldots,L\}$ where reservoirs are attached to $1$ and $L$. Now we assume the hard-core exclusion rule, i.e. $\nu=1$. The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of $gl(N)$. Duality result stated in Subsection \ref{statementDualitySubsection} can be adapted. The extra-sites are denoted by $0$ and $L+1$, and they are connected with sites $1$ and $L$ of the chain respectively. The matrix $R_{x}$ defined in \eqref{Revmatrix} 
reduces to the identity, therefore the relation between the generators of the algebra and its transposed reduces to
\begin{equation}\label{transpostionPropertyFund}
	e_{ab}^T= e_{ba}\dt
Therefore, duality matrix reads
	D=\mathcal{D}_{0}\otimes\prod_{x=1}^{L}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\otimes \mathcal{D}_{L+1}
where $\mathcal{D}_{0}$ and $\mathcal{D}_{L+1}$ are given in \eqref{dualityMatrix2}. 
The elements of this duality matrix are given by
\begin{equation}\label{ElementsDualityMatrixChain}
	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
The dual Hamiltonian is
	\widetilde{H}=\widetilde{H}_{left}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{right}
where $\mathcal{H}$ is defined in \eqref{H-corsivo} and 
\begin{equation}\label{boundary-H-dual-chain}
	\widetilde{H}_{left}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{0}\,e_{Na}^{1}-e_{aa}^{1}\right)\qquad 	\widetilde{H}_{right}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{L+1}\,e_{Na}^{L}-e_{aa}^{L}\right)\dt
In the long-time limit the dual process voids the chain, i.e. all particles of types $\{1,\ldots,N-1\}$ are eventually absorbed at the extra-sites $0$ and $L+1$ and replaced by types $N$. We also notice that, up the the bosonic creation operators $(a^{\dagger})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular. This simplification will be crucial in Sections \ref{sectionIntegrabiliy}.\\
with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. The notation with $\bm{n}$, introduced in Subsection \ref{subsectionGeneratorStr} and the one with $\bm{\tau}$ are related by 
\begin{equation}\label{notation-change-relation}
	n_{a}^{x}=\delta_{\tau_{x},a}
In this notation, the elements of the duality matrix reads
\begin{equation}\label{ElementsDualityMatrixChain_1}
	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities. Consider a dual configuration $\bm{\hat{\xi}}:=\sum_{k=1}^{m}\delta_{s_{k}}^{y_{k}}$ where $s_{k}\in\{1,\ldots,N-1\}$ and $y_{k}\in\{1,\ldots,L\}$ such that $y_{k}<y_{k+1}$ for every $k\in\{1,\ldots,m\}$. Fix an arbitrary initial configuration $\bm{n}$, the elements \eqref{ElementsDualityMatrixChain} of the duality matrix computed in the dual configuration $\bm{\hat{\xi}}$ read
	D(\bm{n},\bm{\hat{\xi}})=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{y_{k}},s_{k}}=1\}}=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\dt
Denoting the $m$-point correlations by $\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]$ we have 
%To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$). Therefore, we have the following equalities
\begin{equation}\label{CorrelationByABS-prob}
\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\hat{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\hat{\xi}}(t))\right]
	\\&=\sum_{c_{1}=0}^{1}\ldots \sum_{c_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}})
\begin{equation}\label{absProbabilitiesIntegrable}
	\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(c_{k}\delta_{0}+(1-c_{k})\delta_{L+1}\right)\lvert \bm{\xi}(0)=\hat{\bm{\xi}}\right)
 namely the joint probability of having, for all $k=1,\ldots,m$, $c_{k}$ particles of species $s_{k}$ at site $y_{k}$ are absorbed at left and $1-c_{k}$ of the same particles absorbed at right. Therefore, by computing these absorption probabilities we determine the arbitrary non-equilibrium steady state correlations of the integrable multi-species stirring process.

@@

with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. The notation with $\bm{n}$, introduced in Subsection \ref{subsectionGeneratorStr} and the one with $\bm{\tau}$ are related by 
	n_{a}^{x}=\delta_{\tau_{x},a}

This notation is equivalent to the one introduced. Indeed, assume that at site $x$ we have a particle of type $a\in\{1,\ldots,N\} $, then $|n^{x}\rangle$ is composed by zeros but in the component $n_{a}^{x}$ where there is $1$. Therefore, we can uniquely associate  $\tau_{x}=a$ to this $|n^{x}\rangle$, denoting the presence of the species $a$ at site $x$. With this notation, we have that 

@@

with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$.

@@

	|\Psi^{''} \rangle=\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
%\begin{equation}\label{ResulsBasis}
%	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}\right)|\mathbf{\bm{\tau}}\rangle

@@

In the first part of the proof we will use the notation with $\bm{n}$, then we will change to the notation with $\bm{\tau}$ at the end of the proof. We recall that these two notations are related by \eqref{notation-change-relation}.  We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutation relations. 

@@

Using the notation $\tau_{x}$, $|\bm{\tau}\rangle $ with $\bm{\tau}$, related to the one with $\bm{n}$ by \eqref{notation-change-relation}, we have 

@@

\Psi^{''}(\tau_1,\ldots,\tau_L)&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2+L-\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+L-x-\sum_{j=x+1}^{L}(1-\delta_{\tau_{j},N})\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},N})\right)}\\
&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(3+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},N})\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},N})\right)}\\
&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}{\Gamma\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}\\
&=  \frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
% &=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\frac{1}{\Gamma(-1)} B(3+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},N}),-1)\\
The last factor only depends on the positions of particles $N$. The $\lambda$-factor depends only on the number of particles of types $1,\ldots,N-1$.

@@

@@

			\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\tau_{x}}^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
%\begin{equation}\label{ABS}
%	\begin{split}
%		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt
%	\end{split}
		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\prod_{x=1}^{L}\lambda_{\tau_{x}}^{c_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}

@@

@@

\textbf{Remark}: By change the summation indices form $c\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}\in \{0,1-\delta_{\tau_{x},N}\}$ and by the by the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as 
\begin{equation}\label{ABS_1}
	\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\dt
 where we used the fact that, for any $\bm{\tau}$ we have 
	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) =\left(2+L-y-\sum_{j=x}^{L}(1-\delta_{\tau_{x},N})\right)
This equation for $\Psi^{'}(\bm{\tau})$ will be useful in the computation of non-equilibrium steady state correlations and in the following Remark, where we specialize it to the case $N=2$ of SSEP. \\ \\
\textbf{Remark:} If we consider the case $N=2$ we have that, for an arbitrary configuration $\bm{\tau}$, we can identify $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites and the remaining $L-|\bm{\tau}|$ empty. We denote by $(x_{i})_{i\in\{1,\ldots,|\bm{\tau}|\}}$ the coordinates of the occupied sites. We introduce $q\in\{0,\ldots,|\bm{\tau}|\}$ and we rewrite \eqref{ABS_1} as

@@

\paragraph{Proof of formula \eqref{ABS-vect}} We have that $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$ (see \eqref{S2-Inverse}), thus we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$. Here it is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and then make explicitly the tensor product over the chain. Using the exponential series, the matrix $\mathcal{S}_{2}$ is given by 

@@

This is a new configuration at site $x$ where, if $x\in\{q_{1},\ldots,q_{i}\}$, the occupation $\tau_{x}$ is replaced by $N$, while it is left uncaged if $x\notin \{q_{1},\ldots,q_{i}\}$. The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation. } 
 By considering a fixed $\langle\bm{\tau}|$, and by using \eqref{goodTP-S2} we obtain 

@@

For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, by using equation \eqref{ResulsBasis} we have
	\Psi^{''}(\bm{\mu})=\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)

@@

 where we have used the fact that 
\begin{equation}
	\left(1+\sum_{j=x}^{L}\delta_{\mu_{j},N}\right) =\left(2+L-y-\sum_{j=x}^{L}(1-\delta_{\mu_{x},N})\right)\co
\end{equation}
Introducing $c_{x}$ defined as 
\begin{equation}
	c_{x}(\mu_{x})=(1-\delta_{\mu_{x},N}) \qquad \forall x\in \{1,\ldots L\}\co
\end{equation}
we obtain 
\begin{equation}\label{coefficients-psiSec}
	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}
\end{equation}
where, for the sake of notation we left understood the dependence on $\mu_{x}$ of $c_{x}$.\\
\end{comment}
\begin{comment}
We introduce the following notation
\begin{equation}\label{notation1}
    e_{ab}=e_{a}^{b}=\left(\delta_{ac}\delta_{bd}\right)_{c,d\in\{1,\ldots,N\}}\qquad \forall a,b\in \{1,\ldots,N\}
\end{equation}
and 
\begin{equation}\label{notation2}
    e_{ab}\otimes e_{cd}=e_{a,c}^{b,d}=\left(\delta_{(a,b),(e,f)}\delta_{(c,d),(g,h)}\right)_{e,f,g,h\in \{1,\ldots,N\}}\qquad \forall a,b,c,d\in \{1,\ldots,N\}
    \end{equation}
    that can be generalized for $e_{\tau_{1},\ldots,\tau_{L}}^{q_{1},\ldots,q_{L}}$ with $\tau_{1},\ldots,\tau_{L},q_{1},\ldots,q_{L}\in \{1,\ldots,N\}$. With this notation we have that

@@

		\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}

@@

\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{y_{1}},\ldots,c_{y_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{y_{k}}}\beta_{s_{k}}^{1-c_{y_{k}}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{y_{j}}\right)\\&\prod_{x=1\,:\,x\notin \{y_{1},\ldots,y_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}c_{y_{k}}\right)
It seems to me that it is more complicated than \eqref{exactCorrelations}...

@@

\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&

@@

The elements of the duality matrix in this integrable case are given in equation \eqref{ElementsDualityMatrixChain_1}. Thus we have that 
